Gammapy: A Python package for gamma-ray astronomy

### 2023-01-24 src/ms-review.tex

\section{Gamma-ray Data Analysis}
\label{sec:gammaray-data-analysis}
% This might not be the bast place compared to introduction
The data reduction process in \gammaray astronomy is usually split into two parts.
The first one deals with the data processing from camera measurement, calibration, event
reconstruction and selection to yield a list of reconstructed \gammaray event candidates.
This sequence, sometimes referred to as low-level analysis, is usually very specific to
a given observation technique and even to a given instrument.

@@

\subsection{Data analysis workflow}
%
\begin{figure*}[h!]
	\centering
	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
	\caption{
		\gammapy sub-package structure and data analysis workflow. The top row
        defines the groups for the different data levels and reduction steps
        from raw gamma-like events on the left, to high level science products
        on the right. The direction of the data flow is illustrated with the
        grey arrows. The gray folder icons represent the different sub-packages
        in \gammapy and their names. Below each icon there is a list of the most
        important objects defined in the sub-package.
    }
	\label{fig:data_flow}
\end{figure*}
%

The first step in \gammaray data analysis is the selection and extraction of observations
based of their metadata including information such as pointing direction, observation
time and observation conditions. The access to the events data and instrument 
reponse per observation is supported by classes and methods
in the \code{gammapy.data} (see Section~\ref{ssec:gammapy-data}) and the \code{gammapy.irf}
(see Section~\ref{ssec:gammapy-irf}) subpackages.

>>>>

\section{Gamma-ray Data Analysis}
%
\begin{figure*}[h!]
	\centering
	\includegraphics[width=1.\textwidth]{figures/data_flow.pdf}
	\caption{
		\gammapy sub-package structure and data analysis workflow. The top row
        defines the groups for the different data levels and reduction steps
        from raw gamma-like events on the left, to high level science products
        on the right. The direction of the data flow is illustrated with the
        grey arrows. The gray folder icons represent the different sub-packages
        in \gammapy and their names. Below each icon there is a list of the most
        important objects defined in the sub-package.
    }
	\label{fig:data_flow}
\end{figure*}
%
\label{sec:gammaray-data-analysis}
% This might not be the bast place compared to introduction
The data reduction process in \gammaray astronomy is usually split into two parts.
The first one deals with the data processing from camera measurement, calibration, event
reconstruction and selection to yield a list of reconstructed \gammaray event candidates.
This sequence, sometimes referred to as low-level analysis, is usually very specific to
a given observation technique and even to a given instrument.

@@

\subsection{Data analysis workflow}
The first step in \gammaray data analysis is the selection and extraction of observations
based of their metadata including information such as pointing direction, observation
time and observation conditions. The access to the events data and instrument 
reponse per observation is supported by classes and methods
in the \code{gammapy.data} (see Section~\ref{ssec:gammapy-data}) and the \code{gammapy.irf}
(see Section~\ref{ssec:gammapy-irf}) subpackages.
